Outbreak response models of vaccine-preventable diseases in humans (1970-2019) - A systematic review (Supplementary Files)

### 2023-04-23 analyses/scripts/orv_sys_rev_supplementary.Rmd
Replaced "%nin%" with !(%in%) to remove unneccesary package dependency

#'Modify the data frame to lump together all countries with less than some number of studies as 'other' and recalculate the percentage studied
countries_studied_by_count_aggregated <- countries_studied_by_count %>% 
  group_by(country_studied) %>%
  summarise(num_of_studies = sum(num_of_studies),
            .groups = 'drop'
            ) %>% 
  filter(country_studied %nin% c('none', 'west_africa', 'global', 'northern_hemisphere', 'southeast_asia', 'who_southeast_asia_region')) %>% 
  arrange(desc(num_of_studies)) %>% 
  adorn_totals(where = c('row')) %>% 
  adorn_percentages(denominator = 'col') %>% 
  adorn_pct_formatting() %>% 
  adorn_ns() %>% 
  ungroup()

>>>>

#'Modify the data frame to lump together all countries with less than some number of studies as 'other' and recalculate the percentage studied
countries_studied_by_count_aggregated <- countries_studied_by_count %>% 
  group_by(country_studied) %>%
  summarise(num_of_studies = sum(num_of_studies),
            .groups = 'drop'
            ) %>% 
  filter(!(country_studied %in% c('none', 'west_africa', 'global', 'northern_hemisphere', 'southeast_asia', 'who_southeast_asia_region'))) %>% 
  arrange(desc(num_of_studies)) %>% 
  adorn_totals(where = c('row')) %>% 
  adorn_percentages(denominator = 'col') %>% 
  adorn_pct_formatting() %>% 
  adorn_ns() %>% 
  ungroup()
